Identifying Pathway Modules from High Throughput Genetic Interaction Data using Simulated Annealing

### 2016-12-12 paper/paper.tex
added reference for funcassociate and simanneal package
added abstract

% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Fogarty, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

@@

% Head 1

% \section{Abstract}

@@

>>>>

@@

\section{Abstract}
We present simulated annealing as an alternative to the LocalCut algorithm outlined in Leiserson \textit{et al} for generating between pathway modules from genetic interaction data. We find that our implementation of simulated annealing does not converge and presents comparable results to a random simulation. We then address the shortcomings of our implementation and possible further steps.

@@

Berriz G. King O. Bryant B., et al. Characterizing gene sets with funcassociate. Bioinformatics. 2003;19:2502–2504.\\

Simanneal package: https://github.com/perrygeo/simanneal\\
